raptr: Representative and Adequate Prioritization Toolkit in R

### 2016-11-28 code/rmarkdown/article.Rmd
+ add tweetable abstract

Short running title: Representative and adequate prioritizations  
Abstract word count: 346 / 350  
Total word count: 6974 / 7000  
Number of references: 42  
Number of figures: 8  
Number of tables: 0  
Number of textboxes: 0  
Number of equations: 4

>>>>

Short running title: Representative and adequate prioritizations
Tweetable abstract: Make smarter spatial conservation decisions that foster biodiversity processes using raptr R package
Abstract word count: 346 / 350  
Total word count: 6974 / 7000  
Number of references: 42  
Number of figures: 8  
Number of tables: 0  
Number of textboxes: 0  
Number of equations: 4
